% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Yi Liu (Steven)}
\newcommand{\CVTitle}{Yi Liu's CV}
\newcommand{\CVNote}{Updated on {\today}.}
\newcommand{\CVWebpage}{https://yliu.io}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.com/maps/place/B033%2C%20Hessert%20Lab%2C%20Univ.%20of%20Notre%20Dame%2C%20Notre%20Dame%2C%20IN%2046545}
{B033, Hessert Lab, Univ. of Notre Dame, Notre Dame, IN 46545}
\par
\href{mailto:yliu27@nd.edu}
{yliu27@nd.edu}
\,\SubBulletSymbol\,
%+1\,(555)\,101-1001
%\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

    \Entry
    \textbf{University of Notre Dame},
    Notre Dame, IN

    \Gap
        \BulletItem
        Ph.D. student in Aerospace \& Mechanical Engineering
        \hfill
        \DatestampY{2016} -- Present
            \begin{Detail}
                        \SubBulletItem
                        GPA: 4.0/4.0
                        \SubBulletItem
                        Advisor: Prof. Meng Wang
                    \SubBulletItem
                    Focus:
                    computational fluid dynamics, turbulence, high-performance computing, aeroacoustics
            \end{Detail}
    \Entry
    \textbf{Syracuse University},
    Syracuse, NY

    \Gap
        \BulletItem
        M.S. in Mechanical \& Aerospace Engineering
        \hfill
        \DatestampY{2013} -- \DatestampY{2015}
            \begin{Detail}
                        \SubBulletItem
                        GPA: 4.0/4.0
                        \SubBulletItem
                        Advisor: Prof. Melissa Green
                    \SubBulletItem
                    Focus:
                    turbulence, dynamical system, geophysical fluid dynamics, high-throughput computing, GPU computing
            \end{Detail}
    \Entry
    \textbf{Tongji University},
    Shanghai, China

    \Gap
        \BulletItem
        B.S. in Automotive Engineering
        \hfill
        \DatestampY{2007} -- \DatestampY{2012}
            \begin{Detail}
                        \SubBulletItem
                        GPA: 86.21/100
                    \SubBulletItem
                    Focus:
                    transportation design, automotive aerodynamics, artificial neural network
            \end{Detail}
        \BulletItem
        Visiting student in Industrial Design at College of Architecture and Urban Planning
        \hfill
        \DatestampY{2007} -- \DatestampY{2009}

%%%%%%%%%%%%%%%%
%% EXPERIENCE %%
%%%%%%%%%%%%%%%%

\Section
{Experience}
{Experience}
{PDF:Experience}

    \Entry
    \textbf{Research Assistant},
    \href{http://www.nd.edu/~flowpac/}{Institute for Flow Physics and Control}, University of Notre Dame
    \hfill
    \DatestampY{2016} -- Present
        \Gap
    \Entry
    \textbf{Research Assistant},
    \href{http://greenfluids.syr.edu/}{Green Fluid Dynamics Lab}, Syracuse University
    \hfill
    \DatestampY{2014} -- \DatestampY{2016}
        \Gap
    \Entry
    \textbf{Computer Programmer},
    Core Infrastructure Services, Syracuse University
    \hfill
    \DatestampY{2015} -- \DatestampY{2016}
        \begin{Detail}
            \BulletItem
            Assisted researchers in Department of Biology by performing bioinformatics programming on OrangeGrid (a high-throughput computing environment on campus) for evolutionary biology researches.
        \end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH PROJECTS %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Selected Research Projects}
{Selected Research Projects}
{PDF:ResearchProjects}

    \Entry
    Wall pressure fluctuations in compressible turbulent channel flows
    \hfill
    \DatestampY{2017} -- Present
    \begin{Detail}
        \BulletItem
        Performing direct numerical simulations (DNS) and large-eddy simulations (LES) to investigate spatiotemporal characteristics of unsteady wall pressure in compressible channel flows.
    \end{Detail}
    \Entry
    Lagrangian coherent structures (LCS) in the Gulf Stream
    \hfill
    \DatestampY{2014} -- \DatestampY{2018}
    \begin{Detail}
        \BulletItem
        Developed programs to calculate the finite-time Lyapunov exponent (FTLE) and Lagrangian-averagedvorticity deviation (LAVD) to find LCS in the Gulf Stream region using altimeter data.
        \BulletItem
        Investigated the transport and mixing properties of the meandering jet and vortices, and the topological changesassociated with the structures.
        \BulletItem
        Code available at \href{https://github.com/stevenliuyi/ocean-ftle}{https://github.com/stevenliuyi/ocean-ftle}.
    \end{Detail}
    \Entry
    Three dimensional LCS in a turbulent channel flow
    \hfill
    \DatestampY{2014} – \DatestampY{2016}
    \begin{Detail}
        \BulletItem
        Computed 3D FTLE fields of the direct numerical simulation (DNS) results of a turbulent channel flow toinvestigate the 3D coherent structures.
        \BulletItem
        Adopted high-throughput computing (HTC) technique to speed up 3D calculations.
        \BulletItem
        Code available at \href{https://github.com/stevenliuyi/3d-ftle}{https://github.com/stevenliuyi/3d-ftle}.
    \end{Detail}
    \Entry
    GPU programming in CFD simulations
    \hfill
    \DatestampY{2015}
    \begin{Detail}
        \BulletItem
        Compared GPU parallel (OpenCL framework) and CPU sequential computing in CFD simulations.
        \BulletItem
        Developed CFD codes to capture shock-waves and tested for two cases (a shock-tube flow simulation and a transonic nozzle flow simulation).
        \BulletItem
        Code available at \href{https://github.com/stevenliuyi/gpu-cfd}{https://github.com/stevenliuyi/gpu-cfd}.
    \end{Detail}
    \Entry
    Aerodynamics of electric vehicles based on CFD and neural network
    \hfill
    \DatestampY{2012}
    \begin{Detail}
        \BulletItem
        Combined artificial neural network, genetic algorithm and CFD simulation to develop a novel method to improve aerodynamics performance in the automobile design process.
    \end{Detail}

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

    \Entry
    \underline{Yi Liu}, Melissa Green, Chris Wilson, Chris Hughes (2018).
        ``\href{https://doi.org/10.1002/2017JC013390}{Gulf Stream Transport and Mixing Processes via Coherent Structure Dynamics},''
    \textit{Journal of Geophysical Research: Oceans}, 123(4), 3014-3037.
    \Gap

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PRESENTATIONS & ABSTRACTS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Presentations\newline\& Abstracts}
{Presentations \& Abstracts}
{PDF:PresentationsAndAbstracts}

    \Entry
    \underline{Yi Liu}, Kan Wang, Meng Wang.
        ``Computation of Wall Pressure Fluctuations in Compressible Turbulent Channel Flows,''
    Mechanics and Applied Science Seminar, University of Notre Dame, Notre Dame, IN, USA. 18 Jan 2019 (scheduled).
    \Gap
    \Entry
    \underline{Yi Liu}, Kan Wang, Meng Wang.
        ``\href{http://meetings.aps.org/Meeting/DFD18/Session/A05.7}{Computation of Wall Pressure Fluctuations in Compressible Turbulent Channel Flows},''
    71st Annual Meeting of the American Physical Society's Division of Fluid Dynamics, Atlanta, GA, USA. 18-20 Nov 2018.
    \Gap
    \Entry
    \underline{Yi Liu}, Chris Wilson, Melissa Green, Chris Hughes.
        ``\href{https://agu.confex.com/agu/os18/meetingapp.cgi/Paper/308347}{Gulf Stream Transport and Mixing Processes via Lagrangian Coherent Structure Dynamics},''
    2018 Ocean Sciences Meeting, Portland, OR, USA. 11-16 Feb 2018.
    \Gap
    \Entry
    Chris Wilson, \underline{Yi Liu}, Melissa Green, Chris Hughes.
        ``\href{https://meetingorganizer.copernicus.org/EGU2017/EGU2017-10345.pdf}{Gulf Stream Transport and Mixing Processes via Coherent Structure Dynamics},''
    European Geosciences Union General Assembly 2017, Vienna, Austria. 23-28 April 2017.
    \Gap
    \Entry
    Chris Wilson, \underline{Yi Liu}, Melissa Green, Chris Hughes.
        ``\href{https://agu.confex.com/agu/os16/meetingapp.cgi/Paper/92464}{An Update to the “Barrier or Blender” Model of the Gulf Stream, Based on Lagrangian Analysis of Aviso Altimetry},''
    2016 Ocean Sciences Meeting, New Orleans, LA, USA. 21-26 Feb 2016.
    \Gap
    \Entry
    \underline{Yi Liu}, Chris Wilson, Melissa Green, Chris Hughes.
        ``\href{https://meetings.aps.org/Meeting/DFD15/Session/R28.5}{Lagrangian Coherent Structures in the Gulf Stream},''
    68th Annual Meeting of the American Physical Society's Division of Fluid Dynamics, Boston, MA, USA. 22-24 Nov 2015.
    \Gap

%%%%%%%%%%%%%%%%%%%%%%
%% HONORS & AWARDS  %%
%%%%%%%%%%%%%%%%%%%%%%

\Section
{Honors \& Awards}
{Honors \& Awards}
{PDF:HonorsAndAwards}

    \BulletItem
    Outstanding Graduate Student of Mechanical \& Aerospace Engineering, Syracuse University
    \hfill
    \DatestampY{2015}
        \begin{Detail}
        \Item
        For ranking first in the program
        \end{Detail}
    \Gap
    \BulletItem
    Member of Honor Society of Phi Kappa Phi
    \hfill
    \DatestampY{2014} -- Present
    \Gap
    \BulletItem
    Graduate Student Scholarship, Syracuse University
    \hfill
    \DatestampY{2013} -- \DatestampY{2015}
    \Gap
    \BulletItem
    Outstanding Student Scholarship, Tongji Unversity
    \hfill
    \DatestampY{2008}, \DatestampY{2009}
    \Gap

\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\BigGap
\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]

\end{document}